---
title: "Hypothesis Testing Worksheet"
author: "Morgan Holland"
date: "6/3/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
```

**Instructions**: Test the following hypotheses about the population mean. I strongly recommend you draw a picture for each one to be sure you understand where the test statistic, critical value, $\alpha$ level, and p-value lie on the standard normal distribution.

```{r, include=FALSE}
source('xbarscript.R')
set.seed(1234)
```

```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`
    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`
    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`    
```{r}
t <- testgen(sample(1:10000,1))
mu <- t$mu
n <- t$n
xbar <- t$xbar
s <- t$s
testtxt <- t$testtxt
result <- t$result
alpha <- t$alpha
```

1. Suppose you have a sample of $n = `r n`$ observations of a variable $X$. You calculate $\overline X = `r xbar`$ and $s = `r s`$. Test the hypothesis that $\mu `r testtxt` `r mu`$ at $\alpha = `r alpha`$

    SOLUTION: `r result`